Object-Oriented Internet - Azure interoperability

### 2020-10-08 Latex/Manuscript.tex
Adopt jacs-paper-template #32
- applied template setting to the Manuscript.tex
- refactoring names

\documentclass{article}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}

@@

\title{Object-Oriented Internet - Azure interoperability}
% \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
\author[1]{Mariusz Postół}
\author[2]{Piotr Szymczak}
\author[3]{Clemens Vasters}
\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
% \email{mailto:mariusz.postol@p.lodz.pl} 
\affil[3]{Microsort}
%\tocauthor{Mariusz Postół}
%\institute{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \email{mailto:mariusz.postol@p.lodz.pl} }

@@

\begin{abstract}

TBD

\end{abstract}

@@

\bibliography{Manuscript}
\bibliographystyle{splncs04}

>>>>

\documentclass{jacsart}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}

\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}

@@

\title{Object-Oriented Internet - Azure interoperability}
% \title{Object-Oriented Internet - reactive visualization of asynchronous data using AZURE}
\headtitle{OOI - Azure interoperability}

%\author[1]{Mariusz Postół}
%\author[2]{Piotr Szymczak}
%\author[3]{Clemens Vasters}
%\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
% \email{mailto:mariusz.postol@p.lodz.pl} 
%\affil[3]{Microsort}
%\tocauthor{Mariusz Postół}
%\institute{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \email{mailto:mariusz.postol@p.lodz.pl} }

\author{Author One\inst{1}, Author Two\inst{1,2}}
\headauthor{A. One, A. Two}
\affiliation{%
  \inst{1}Name of the Unit represented (e.g. Your University)\\
  Faculty/Department/Office Name\\
  Postal Addres with the zip-code\\
  yourid@your.mail.server
  \andinst
  \inst{2}Name of the Unit represented (e.g. Your University)\\
  Faculty/Department/Office Name\\
  Postal Addres with the zip-code\\
  yourid@your.mail.server}

@@

\begin{abstract}
Each paper should be followed by a compact abstract which points to the main
scopes and the results obtained by the paper. The abstract should be written
with the Times New Roman font, 10 pt, justified, and with the 1cm margin both
left and right side with respect  to the margin of the paper. The abstract should not contain any formulas or references, and should not exceed 200 words. 
\end{abstract}

@@

\bibliography{Manuscript}
\bibliographystyle{aiaa-jacs.bst}
